Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-01 paper/related_work.tex
related work

Supervised latent Dirichlet allocation (sLDA) builds on LDA by incorporating
an exponential family response variable. Although there are many models
for making predictions based on free text, sLDA is unique in that
it is a generative model, it represents documents as a mixed-membership,
and constrains the inference of the latent structure of the documents
by its predictability of the response variable. In other words, sLDA
infers topics such that the model is capable of a high predictive
likelihood for words in a document and the response variable associated
with a document. This approach has been shown to outperform both LASSO
(L1 regularized least squares regression) and LDA followed by least
squares regression \citep{BleiMcAuliffe2008}.

There have been many models that incorporate both latent models of
text and some form of supervision \citep{Ramage2009,DiscLDA,wangbleifeifei08,RelationalLDA}.
One set of models that are particularly relevant to HSLDA are Chang
and Blei's hierarchical models for document networks (Relational Topic
Models). In that family of models, they encountered a similar scenario
where the lack of a link did not truly indicate absence. In hierarchically
labeled data, negative labels are uncommon and the lack of a label
in the hierarchy is not equivalent to a negative label. Therefore,
as in the work of Chang and Blei, we employ regularization to account
for the lack of negative labels. This will be discussed further in
\ref{sec:model}.

>>>>

Supervised latent Dirichlet allocation (sLDA) builds on LDA by incorporating
supervision in the form of an observed exponential family response 
variable per document. As a result, sLDA
infers topics such that the model predicts the response variable while
improing word likelihood.  This approach has been shown to outperform both LASSO
(L1 regularized least squares regression) and LDA followed by least
squares regression \citep{BleiMcAuliffe2008}.

Other models that incorporate both and some form of supervision include
LabeledLDA\citep{Ramage2009}, DiscLDA\citep{DiscLDA}, models applied to 
computer vision and document networks\citep{wangbleifeifei08,RelationalLDA}.

%One set of models that are particularly relevant to HSLDA are Chang
%and Blei's hierarchical models for document networks (Relational Topic
%Models). In that family of models, they encountered a similar scenario
%where the lack of a link did not truly indicate absence. In hierarchically
%labeled data, negative labels are uncommon and the lack of a label
%in the hierarchy is not equivalent to a negative label. Therefore,
%as in the work of Chang and Blei, we employ regularization to account
%for the lack of negative labels. This will be discussed further in
\ref{sec:model}.
